refnx - Neutron and X-ray reflectometry analysis in Python

### 2018-07-16 paper/manuscript.tex
PAPER

The posterior probability distribution in Bayesian statistics, Equation~\ref{eqn:1}, says the posterior probability distribution for the parameters is proportional to the product of the prior knowledge of the parameters and the likelihood (or the sum of the log-probabilities).

@@

\subsection*{Example}
Neutron reflectometry is an ideal technique for the study of biologically relevant lipid membrane mimics and their interactions with proteins, etc. Multiple contrast variation measurements are necessary to reduce modelling ambiguity (due to loss of phase information) and improve the ability to determine the structure of various components in the system. The gold standard approach for analysis of these datasets is co-refinement with a common model, and to parameterise the model in terms of chemically relevant parameters, such as area per molecule. Sometimes a patchy coverage (distinct to low area per molecule) necessitates the use of an (incoherent) sum of reflectivities from different areas. \refnx has functionality for all these requirements, such as the \LipidLeaflet component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel. It is straightforward to develop/modify new components for different structural functionality, a consequence of the object-oriented approach. Here the \LipidLeaflet is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}. The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of 57$\AA\pm1$. Figures~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} show the probability distribution of the generative model around the data and in the SLD profile. These are obtained by random samples from the MCMC chain. The spread in SLD profiles is used to determine what range of structures is consistent with the data. Multi-modalities in these SLD profiles can be due to statistical uncertainties, the Q ranges measured, and the loss of phase information in NR \cite{Majkrzak1999, Heinrich2009}.
%TODO use exact area per molecule, and use a reference for the Xray analysis

>>>>

The posterior probability distribution in Bayesian statistics, Equation~\ref{eqn:1}, says the posterior probability distribution for the parameters is proportional to the product of the prior probability and the likelihood (or the sum of the log-probabilities).

@@

\subsection*{Example}
Neutron reflectometry is an ideal technique for the study of biologically relevant lipid membrane mimics and their interactions with proteins, etc. Multiple contrast variation measurements are necessary to reduce modelling ambiguity (due to loss of phase information in the scattering experiment) and improve the ability to determine the structure of various components in the system. The gold standard approach for analysis of these datasets is co-refinement with a common model, and to parameterise the model in terms of chemically relevant parameters, such as area per molecule. Sometimes a patchy coverage (distinct to low area per molecule) necessitates the use of an (incoherent) sum of reflectivities from different areas. \refnx has functionality for all these requirements, such as the \LipidLeaflet component for describing the head and tail groups of a lipid leaflet, and \MixedReflectModel. It is straightforward to develop/modify new components for different structural functionality, a consequence of the object-oriented approach. Here the \LipidLeaflet is used to co-refine three contrasts (\ce{D_2O}, \ce{Si} contrast match [hdmix, SLD=$2.07\times10^{-6}\AA^{-2}$], and \ce{H_2O}) of a 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC) bilayer at the solid-liquid interface, Figure \ref{fig:global_fit} \footnote{The validity of \LipidLeaflet does depend on the area per molecule being equal for the headgroup and tailgroup regions, as pointed out by Gerelli \cite{Gerelli2016}, which can be violated if there are guest molecules that insert in the membrane.}. The corner plot (Figure \ref{fig:corner}) produced from the MCMC analysis shows the covariance between parameters, with an area per molecule of 57$\AA\pm1$. Figures~\ref{fig:global_fit} and \ref{fig:d2o_sld_spread} show the probability distribution of the generative model around the data and in the SLD profile. These are obtained by random samples from the MCMC chain. The spread in SLD profiles is used to determine what range of structures is consistent with the data. Multi-modalities in these SLD profiles can be due to statistical uncertainties, the Q ranges measured, and the loss of phase information in NR \cite{Majkrzak1999, Heinrich2009}.
%TODO use exact area per molecule, and use a reference for the Xray analysis
